Collaborative Visual Analysis on the Web with RCloud

### 2015-06-26 discussion.tex
bibliography fixes
fixes

\paragraph*{Modularity and granularity} Modularity, or the ability
to partition work into independent units, is a key to working
productively in teams.
It is a benefit if the units can be kept small or granular, so team members
can realize benefits at least proportional to the work on the units.
RCloud's notebook and versioning allow work to be divided
into units as fine as the underlying language allows, and
encourage making incremental changes at low cost and without disrupting
the work of others.

@@

\paragraph*{Nonforgetful, effortless exploration is hard}
Users reported that RCloud's combined notebook and command line
interface interferes with their familiar use of R for exploration. In
current R practice, the command prompt is used to try things out. It
is very fast and there is often no commitment: nothing gets saved by
default, and clean up is automatic. In contrast, in RCloud's
notebook interface, cells generated doing exploration are saved in the
notebook. We arrived here from an insistence on reproducibility: it is a
core principle that no command should be run without being
saved. In our experience some history steps are only found to be
important in hindsight, and deleting history by default makes it too
easy to lose those steps by accident.

% Surprisingly, we found that when users realize that \emph{scratch work
We found that when users realize that \emph{scratch work
is getting saved}, it sheer volume becomes burdensome.
Clearly, RCloud is an extreme, and the right solution is
probably in the middle. An intriguing possibility,
suggested by one of our interviewees, is to implement auditing of data
analyses as it existed in S~\cite{Becker:1988:Auditing}, tying
data artifacts to the processes that generated them. 
Bookkeeping would be reduced to selecting the \emph{data} to be kept,
and the code that generated it would be derived and saved transparently.

>>>>

\paragraph*{Modularity and granularity} Modularity, or the ability
to partition work into independent units, is a key to working
productively in teams.
If the units can be kept small or granular, team members
can realize benefits at least proportional to their work on the units.
RCloud's notebook and versioning allow work to be divided
into units as fine as the underlying language allows, and
encourage making incremental changes at low cost and without disrupting
the work of others.

@@

\paragraph*{Nonforgetful, effortless exploration is hard}
Users reported that RCloud's interface clashes with the
typical use of R for exploration.
In current R practice, the command prompt is used to try things out.
It is very fast and there is often no commitment: nothing gets saved by
default, and clean up is automatic. In contrast, in RCloud,
cells generated during exploration are saved in notebooks.
We arrived at this from an insistence on reproducibility: 
no command should be run without being saved.
In our experience, some history steps are only found to be
important in hindsight, and deleting history by default makes
it too easy to lose those steps by accident.

% Surprisingly, we found that when users realize that \emph{scratch work
We found that when users realize that \emph{scratch work
is getting saved}, its sheer volume becomes burdensome.
Clearly, RCloud is an extreme, and the right solution is
probably in the middle. An intriguing possibility,
suggested by one of our interviewees, is to implement auditing of data
analyses as it existed in S~\cite{Becker:1988:Auditing}, tying
data artifacts to the processes that generated them. 
Bookkeeping would be reduced to selecting the \emph{data} to be kept,
and the code that generated it would be derived and saved transparently.
